### 2018-02-28 Docs/analysis/analysis.tex

The {\tt BoxLib/Tools/Postprocessing/F\_Src/} directory contains a large
number of Fortran-based analysis routines for BoxLib datasets.  Many
of these can be used with both \maestro\ and the compressible
astrophysics code, \castro.

@@

The following routines are generally applicable for any BoxLib-based
plotfile.  Typing the executable names without any arguments will
provide usage examples.

@@

@@

{\tt fspeciesmass2d.f90} should provide a good starting point for
writing a new analysis routine for BoxLib data.

>>>>

The {\tt amrex/Tools/Postprocessing/F\_Src/} directory contains a large
number of Fortran-based analysis routines for AMReX datasets.  Many
of these can be used with both \maestro\ and the compressible
astrophysics code, \castro.

@@

The following routines are generally applicable for any AMReX-based
plotfile.  Typing the executable names without any arguments will
provide usage examples.

@@

  With the optional {\tt --zone\_info var} argument, where {\tt var}
  is the name of a variable, it will also report the full state
  for the zone where {\tt var} has the largest error.

@@

{\tt fspeciesmass2d.f90} should provide a good starting point for
writing a new analysis routine for AMReX data.
